Relation of SARS-CoV-2 variant B.1.1.7 to transmission-related factors and to severity of COVID-19 in Scotland: REACT-SCOT case-only linkage study [follow-up to `r dateformat(min(maxdate.death, lastdate.rapid))`]

### 2021-03-06 ct.Rmd
updates to ct draft

# Methods
## Ascertainment of COVID-19 cases evaluable for B.1.1.7 status
From early in the epidemic Public Health Scotland has maintained a regularly-updated case-control study (REACT-SCOT) of all COVID-19 cases in Scotland, with each case matched to up to ten controls and extensive linkage to other health care records and routine datasets   as previously reported [@mckeigue_rapid_2020-1].  The case definition in REACT-SCOT includes all those with a positive nucleic acid test, a hospital admission with a discharge code of COVID-19  or a death certificate with mention of COVID-19.  For cases who had tested positive in a Lighthouse laboratory, cycle threshold (Ct) values for each channel were available.  The analyses presented here focus on the subset of cases evaluable for S gene dropout as described below. As these analyses did not use data on controls, the description of methods is restricted to case ascertainment and linkages in REACT-SCOT.

@@

## Imputation of B.1.1.7 status from S gene signal
The ThermoFisher TaqPath assay scores results as positive if there are detectable signals from at least two of the three genes: S, N, and ORF1ab.  For this study test-positive cases with a detectable S gene signal were scored as "No dropout". Test-positive cases with no S gene signal were scored as "Definite dropout" if the cycle thresholds for the ORF1ab and N genes were less than 30. All other positive test results with no signal from the S gene were scored as "Undetermined". 
 <!--Test-positive cases with no S gene signal were scored as "Definite dropout" if the Ct for the ORF1ab  gene (\ensuremath{C_{ORF}}) was less than 31, the Ct for the N gene (\ensuremath{C_{N}}) was less than 30, and \ensuremath{C_{ORF} - C_{N} > - 1}. All other positive test results with no signal from the S gene were scored as "Undetermined".   This was based on using the results of repeat tests on the same individual to reclassify borderline results as described in the Supplementary Text.

Chris R: a positive for STGF defined as  negative on the S gene and Ct < 25 for at least one of the OR and N genes.  A weak positive is negative for S gene and Ct <= 30 for both OR and N gene. --->

@@

The proportion of cases with fatal outcome was calculated over sliding seven-day time windows.  We denote this fraction as the fatal case proportion.  We use this term  to distinguish it from the case fatality ratio which is classically defined without linkage between diagnoses and deaths, as the ratio of deaths from the disease to diagnosed cases over a specified time window. Data were available up to  `r dateformat(lastdate.rapid)` for hospital admissions, `r dateformat(maxdate.sicsag)`  for entry to critical care and `r dateformat(maxdate.death)` for death registrations.

## Ascertainment of exposure  to  other  COVID-19 risk settings or exposures 
All cases were linked to the CHI database that contains addresses linked to the Unique Property Reference Number, care home status, and the ages of all household members.  Socioeconomic status was assigned as the Scottish Index of Multiple Deprivation (SIMD) score which is based on linkage of postcodes to Census data [@fraser_scottish_2020].  Quintile 5 is the least deprived. Care home residence was assigned using the field in the CHI database,   augmented by coding as care home residents the `r care.home.reclassified[1]` individuals aged over 70 in households with 10 or more adults to give a total of `r cc.all[care.home=="Care/nursing home", .N]` care home residents out of the `r cc.all[, .N]` cases.

@@

Teachers were identified as individuals of working-age registered with the General Teaching Council of Scotland and currently working, or believed to be currently working, as teachers at a Scottish school in 2020. Healthcare workers were identified using the General Practitioner Contractor Database (GPCD) and Scottish Workforce Information Standard System (SWISS) databases as described previously. [@shah_risk_2020; @mcallister_report_2020]. Prior comorbidities were derived by linkage to prescribing and SMR01 as described previously  [@mckeigue_rapid_2020-1].

@@

## Implications for policy 
These results do not indicate that the variant has been preferentially transmitted to those who are exposed to school-age children.  They are also reassuring with respect to concerns that the variant may be associated with more severe disease.  Even if the higher transmissibility of the variant increases the incidence of infections, the effect on severe disease is likely to be small in comparison to the effect of other factors that are amenable to intervention, including overprescribing of psychotropic drugs [@mckeigue_relation_2021], transmission in hospitals[@mckeigue_relation_2021-1], and vaccination of vulnerable individuals.

@@

# Registration
The original protocol for the REACT-SCOT case-control study was registered with the European Network of Centres for Pharmacoepidemiology and Pharmacovigilance (ENCEPP number EUPAS35558).

@@

## Acknowledgements
We thank all staff in critical care units who submitted data to the SICSAG database, the Scottish Morbidity Record Data Team, the staff of the National Register of Scotland, the Public Health Scotland Terminology Services, the HPS COVID-19 Laboratory & Testing cell and the NHS Scotland Diagnostic Virology Laboratories, and Nicola Rowan (HPS) for coordinating this collaboration.

## Public Health Scotland COVID-19 Health Protection Study Group
<!--this group needs to be updated-->

Alice Whettlock$^1$, Allan McLeod$^1$, Andrew Gasiorowski$^1$, Andrew Merrick$^1$, Andy McAuley$^1$, April Went$^1$, Calum Purdie$^1$, Colin Fischbacher$^1$, Colin Ramsay$^1$, David Bailey$^1$, David Henderson$^1$, Diogo Marques$^1$, Eisin McDonald$^1$, Genna Drennan$^1$, Graeme Gowans$^1$, Graeme Reid$^1$, Heather Murdoch$^1$, Jade Carruthers$^1$, Janet Fleming$^1$, Jade Carruthers$^1$, Joseph Jasperse$^1$, Josie Murray$^1$, Karen Heatlie$^1$, Lindsay Mathie$^1$, Lorraine Donaldson$^1$, Martin Paton$^1$, Martin Reid$^1$, Melissa Llano$^1$, Michelle Murphy-Hall$^1$, Paul Smith$^1$, Ros Hall$^1$, Ross Cameron$^1$, Susan Brownlie$^1$, Adam Gaffney$^2$, Aynsley Milne$^2$, Christopher Sullivan$^2$, Edward McArdle$^2$, Elaine Glass$^2$, Johanna Young$^2$, William Malcolm$^2$, Jodie McCoubrey $^2$

1 Public Health Scotland, Meridian Court, 5 Cadogan Street, Glasgow G2 6QE.

2 NHS National Services Scotland, Meridian Court, 5 Cadogan Street, Glasgow G2
6QE.

@@

```{r plotvariantbydate, echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "H", fig.asp=1.25, fig.cap="\\label{fig:variantbydate}(a) Test-positives by date: area plot showing proportion of S gene dropouts in positive tests with reporting of cycle threshold. (b) Median cycle thresholds (reverse scale) in positive tests by date "}

@@

```{r coeffsexposure, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(table.coeffs.exposure, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="coeffsexposure",
             row.names=TRUE,
             align=c("r", "r", "r", "l", "r", "l"), 
             col.names=c(clean.header(colnames(table.coeffs.exposure)[1:2]),
                         "Odds ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Odds ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Logistic regression of S gene dropout on transmission-related factors") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariable"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.7cm") %>%
    column_spec(column=6, width="2.7cm") %>%
    column_spec(column=7, width="1.7cm") %>%
    add_footnote(label=c("Excluding those with undetermined status for S gene dropout",
                         "Unconditional logistic regression with S gene dropout as dependent variable",
                         "Univariate odds ratios are for models with single variable + week of specimen as categoric variable", 
                         "Multivariable odds ratios are for model with all covariates + week of specimen as categoric variable",
                         "PF, patient-facing"),
                 notation="none") %>%
    kableExtra::group_rows("Age group", 1, 5, bold=FALSE) %>%
    kableExtra::group_rows("Region", 7, 10, bold=FALSE) %>%
    kableExtra::group_rows("Number of adults in household", 13, 17, bold=FALSE) %>%
    kableExtra::group_rows("Number of school-age children in household", 19, 21, bold=FALSE) %>%
    kableExtra::group_rows("Occupation", 22, 25, bold=FALSE) %>%

@@

```{r coxsevere, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(table.severe.coxph, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="coxsevere",
             row.names=TRUE,
             align=c("r", "r", "r", "l", "r", "l"), 
             col.names=c(clean.header(colnames(table.severe.coxph)[1:2]),
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Death or entry to critical care within 28 days of testing positive: Cox regression of time to failure on S gene dropout and covariates") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariable"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.7cm") %>%
    column_spec(column=6, width="2.7cm") %>%
    column_spec(column=7, width="1.7cm") %>%
    add_footnote(label=c("Excluding those with undetermined status for S gene dropout",
                         "Stratified by days since testing positive and calendar week",
                          "Univariate rate ratios are for models with single variable + week of specimen as categoric variable", 
                        "Multivariable rate ratios are for model with all covariates"),
                 notation="none") %>%
    kable_styling(latex_options=c("scale_down", "hold_position"))

@@

knitr::kable(table.hosp.coxph, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="coxhosp",
             row.names=TRUE,
             align=c("r", "r", "r", "l", "r", "l"), 
             col.names=c(clean.header(colnames(table.hosp.coxph)[1:2]),
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Death or hospitalisation within 28 days of testing positive: Cox regression on S gene dropout and covariates") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariable"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.7cm") %>%
    column_spec(column=6, width="2.7cm") %>%
    column_spec(column=7, width="1.7cm") %>%
    add_footnote(label=c("Excluding those with undetermined status for S gene dropout",
                         "Stratified by days since testing positive and calendar week",
                         "Univariate rate ratios are for models with single variable + week of specimen as categoric variable", 
                         "Multivariable rate ratios are for model with all covariates + week of specimen as categoric variable"),
                 notation="none") %>%
    kable_styling(latex_options=c("scale_down", "hold_position"))

@@

# Imputation of S gene dropout

@@

# Supplementary Figures

@@

```{r checkcutoff, echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "H", fig.asp=1, fig.cap="\\label{fig:plotcheck}Test results with S gene signal absent that were originally classified as Undetermined (\\ensuremath{C_{ORF} >= 31 or \\ensuremath{C_{N} >= 31 or  \\ensuremath{C_{N} - C_{ORF} < 1.5}), colour coded by result at repeat test. New separation lines at \\ensuremath{C_{N} - C_{ORF} = 3} and ORF = 33, used in this analysis, are shown in green"}

@@

gA <- ggplotGrob(p.rateratio)
gB <- ggplotGrob(p.region)
gC <- ggplotGrob(p.hcw)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB, gC))

@@

# Supplementary Tables

@@

knitr::kable(table.cases.bymonth, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="casebymonth",
             row.names=TRUE,
             align=rep("r", 5),
             caption="Cases by month") %>%
    add_footnote(label=c("Restricted to cases with specimen date no earlier than 1 Sep 2020",
                         "Outcome is not yet evaluable for cases with specimen date after 31 December 2020"),
                 notation="none") %>%
    kableExtra::group_rows("All cases", 1, 8) %>%
        kableExtra::group_rows("Test-positive cases", 9, 11, bold=FALSE) %>%
        kableExtra::group_rows("Cases with Ct results", 12, 16, bold=FALSE) %>%
        kableExtra::group_rows("Fatal cases and cohort fatality rates by S gene dropout status", 17, 18, bold=FALSE) %>%
        kable_styling(latex_options=c("scale_down", "hold_position"))

>>>>

# Methods
## Ascertainment of COVID-19 cases evaluable for B.1.1.7 status
From early in the epidemic Public Health Scotland has maintained a regularly-updated case-control study (REACT-SCOT) of all COVID-19 cases in Scotland, with each case matched to up to ten controls and extensive linkage to other health care records and routine datasets   as previously reported [@mckeigue_rapid_2020].  The case definition in REACT-SCOT includes all those with a positive nucleic acid test, a hospital admission with a discharge code of COVID-19  or a death certificate with mention of COVID-19.  For cases who had tested positive in a Lighthouse laboratory, cycle threshold (Ct) values for each channel were available.  The analyses presented here focus on the subset of cases evaluable for S gene dropout as described below. As these analyses did not use data on controls, the description of methods is restricted to case ascertainment and linkages in REACT-SCOT.

@@

## Imputation of B.1.1.7 status from S gene signal
The ThermoFisher TaqPath assay scores results as positive if there are detectable signals from at least two of the three genes: S, N, and ORF1ab.  For this study test-positive cases with a detectable S gene signal were scored as "No dropout". Test-positive cases with no S gene signal were scored as "Definite dropout" if the cycle thresholds for the ORF1ab and N genes were less than 30. All other positive test results with no signal from the S gene were scored as "Undetermined". 
 <!--Test-positive cases with no S gene signal were scored as "Definite dropout" if the Ct for the ORF1ab  gene (\ensuremath{C_{ORF}}) was less than 31, the Ct for the N gene (\ensuremath{C_{N}}) was less than 30, and \ensuremath{C_{ORF} - C_{N} > - 1}. All other positive test results with no signal from the S gene were scored as "Undetermined".   This was based on using the results of repeat tests on the same individual to reclassify borderline results as described in the Supplementary Text. 
Chris R: a positive for STGF defined as  negative on the S gene and Ct < 25 for at least one of the OR and N genes.  A weak positive is negative for S gene and Ct <= 30 for both OR and N gene. --->

@@

The proportion of cases with fatal outcome was calculated over sliding seven-day time windows.  Data were available up to  `r dateformat(lastdate.rapid)` for hospital admissions, `r dateformat(maxdate.sicsag)`  for entry to critical care and `r dateformat(maxdate.death)` for death registrations.

## Ascertainment of exposure  to  other  COVID-19 risk settings or exposures 
All cases were linked to the CHI database that contains addresses linked to the Unique Property Reference Number, care home status, and the ages of all household members.  Socioeconomic status was assigned as the Scottish Index of Multiple Deprivation (SIMD) score which is based on linkage of postcodes to Census data [@fraser_scottish_2020].  Quintile 5 is the least deprived. Care home residence was assigned using the field in the CHI database,   augmented by coding as care home residents the `r care.home.reclassified[1]` individuals aged over 70 in households with 10 or more adults to give a total of `r cc.all[care.home=="Care/nursing home", .N]` care home residents out of the `r cc.all[, .N]` cases. The definition of Scottish regions was based on the Nomenclature of Units for Territorial Statistics [Level 2](https://www.gov.scot/publications/review-nomenclature-units-territorial-statistics-nuts-boundaries/), with the North-Eastern and Highlands & Islands regions grouped as Northern.

@@

Teachers were identified as individuals of working-age registered with the General Teaching Council of Scotland and currently working as teachers at a Scottish school in 2020. Healthcare workers were identified using the General Practitioner Contractor Database (GPCD) and Scottish Workforce Information Standard System (SWISS) databases as described previously. [@shah_risk_2020; @mcallister_report_2020]. Prior comorbidities were derived by linkage to prescribing and SMR01 as described previously  [@mckeigue_rapid_2020].

@@

## Implications for policy 
These results do not indicate that the variant has been preferentially transmitted to those who are exposed to school-age children.  They are also reassuring with respect to concerns that the variant may be associated with more severe disease.  Even if the higher transmissibility of the variant increases the incidence of infections, the effect on severe disease is likely to be small in comparison to the effect of other factors that are amenable to intervention, including overprescribing of psychotropic drugs [@mckeigue_relation_2021], transmission in hospitals (McKeigue 2021, submitted) and vaccination of vulnerable individuals.

@@

## Registration
The original protocol for the REACT-SCOT case-control study was registered with the European Network of Centres for Pharmacoepidemiology and Pharmacovigilance (ENCEPP number EUPAS35558).

@@

## Acknowledgements
We thank all staff in critical care units who submitted data to the SICSAG database, the Scottish Morbidity Record Data Team, the staff of the National Register of Scotland, the Public Health Scotland Terminology Services, the HPS COVID-19 Laboratory & Testing cell and the NHS Scotland Diagnostic Virology Laboratories.

## Public Health Scotland COVID-19 Health Protection Study Group
Allan McLeod​, Alice Whettlock April Went, Beth Findlay Chris Sullivan, Ciaran Harvey, David Henderson, Edward McArdle, Eisin McDonald, Emily Griffiths, Genna Drennan, Johanna Young, Kirstin Leslie, Leonardo I Green, Louise Nicol, Melissa Llano, Nick Christofidis, Paul Bett, Ross Cameron, Theresa Ryan, Victoria Ponce Hardy.  
Public Health Scotland, Meridian Court, 5 Cadogan Street, Glasgow G2 6QE

@@

```{r plotvariantbydate, echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "H", fig.asp=1.25, fig.cap="\\label{fig:variantbydate}(a) Test-positive cases with reporting of cycle threshold, by date: area plot showing proportion of S gene dropouts. (b) Median cycle thresholds (reverse scale) in positive tests, by date."}

@@

```{r coeffsexposure, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(table.coeffs.exposure, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="coeffsexposure",
             row.names=TRUE,
             align=c("r", "r", "r", "l", "r", "l"), 
             col.names=c(clean.header(colnames(table.coeffs.exposure)[1:2]),
                         "Odds ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Odds ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Logistic regression of S gene dropout on transmission-related factors") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariable"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.7cm") %>%
    column_spec(column=6, width="2.7cm") %>%
    column_spec(column=7, width="1.7cm") %>%
    add_footnote(label=c("Excluding those with undetermined status for S gene dropout",
                         "Unconditional logistic regression with S gene dropout as dependent variable",
                         "Univariate odds ratios are for models with single variable + week of specimen as categoric variable", 
                         "Multivariable odds ratios are for model with all covariates + week of specimen as categoric variable",
                         "PF, patient-facing"),
                 notation="none") %>%
    kableExtra::group_rows("Age group", 1, 5, bold=FALSE) %>%
    kableExtra::group_rows("Region", 7, 10, bold=FALSE) %>%
    kableExtra::group_rows("Risk category", 13, 15, bold=FALSE) %>%
    kableExtra::group_rows("Number of adults in household", 16, 20, bold=FALSE) %>%
    kableExtra::group_rows("Number of school-age children in household", 21, 23, bold=FALSE) %>%
    kableExtra::group_rows("Occupation", 24, 28, bold=FALSE) %>%

@@

```{r coxsevere, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(table.severe.coxph, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="coxsevere",
             row.names=TRUE,
             align=c("r", "r", "r", "l", "r", "l"), 
             col.names=c(clean.header(colnames(table.severe.coxph)[1:2]),
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Death or entry to critical care within 28 days of testing positive: Cox regression of time to failure on S gene dropout and covariates") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariable"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.7cm") %>%
    column_spec(column=6, width="2.7cm") %>%
    column_spec(column=7, width="1.7cm") %>%
    add_footnote(label=c("Excluding those with undetermined status for S gene dropout",
                         "Stratified by days since testing positive and calendar week",
                          "Univariate rate ratios are for models with single variable + week of specimen as categoric variable", 
                        "Multivariable rate ratios are for model with all covariates"),
                 notation="none") %>%
    kable_styling(latex_options=c("scale_down", "HOLD_position"))

@@

knitr::kable(table.hosp.coxph, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="coxhosp",
             row.names=TRUE,
             align=c("r", "r", "r", "l", "r", "l"), 
             col.names=c(clean.header(colnames(table.hosp.coxph)[1:2]),
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value",
                         "Rate ratio (95\\% CI)", "\\ensuremath{p}-value"), 
             caption="Death or hospitalisation within 28 days of testing positive: Cox regression on S gene dropout and covariates") %>%
    add_header_above(c(" "=3, "Univariate"=2, "Multivariable"=2)) %>%
    column_spec(column=1, width="3cm") %>%
    column_spec(column=2, width="2cm") %>%
    column_spec(column=3, width="2cm") %>%
    column_spec(column=4, width="2.5cm") %>%
    column_spec(column=5, width="1.7cm") %>%
    column_spec(column=6, width="2.7cm") %>%
    column_spec(column=7, width="1.7cm") %>%
    add_footnote(label=c("Excluding those with undetermined status for S gene dropout",
                         "Stratified by days since testing positive and calendar week",
                         "Univariate rate ratios are for models with single variable + week of specimen as categoric variable", 
                         "Multivariable rate ratios are for model with all covariates + week of specimen as categoric variable"),
                 notation="none") %>%
    kable_styling(latex_options=c("scale_down", "HOLD_position"))

@@

# Supplementary material
## Imputation of S gene dropout

@@

## Supplementary Figures

@@

```{r checkcutoff, echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "H", fig.asp=1, fig.cap="\\label{fig:plotcheck}Repeat tests on same individual for test-positive results originally classified as Undetermined (\\ensuremath{C_{ORF} \\ge 31} or \\ensuremath{C_N \\ge 31} or  \\ensuremath{C_N - C_{ORF} < 1.5}), colour coded by result at repeat test. New separation lines at \\ensuremath{C_N - C_{ORF} = 3} and \\ensuremath{C_{ORF} = 33}, used in this analysis, are shown in green"}

@@

gA <- ggplotGrob(p.rateratio)
gB <- ggplotGrob(p.region)
gC <- ggplotGrob(p.hosp)
grid::grid.newpage()
grid::grid.draw(rbind(gA, gB, gC))

@@

## Supplementary Tables

@@

knitr::kable(table.cases.bymonth, 
             escape=FALSE, 
             booktabs=TRUE,
			 label="casebymonth",
             row.names=TRUE,
             align=rep("r", 5),
             caption="Cases by month") %>%
    add_footnote(label=c("Restricted to cases with specimen date no earlier than 1 Sep 2020"),
                 notation="none") %>%
    kableExtra::group_rows("All cases", 1, 8) %>%
        kableExtra::group_rows("Test-positive cases", 9, 12, bold=FALSE) %>%
        kableExtra::group_rows("Cases with Ct results", 13, 16, bold=FALSE) %>%
        kableExtra::group_rows("Fatal cases and cohort fatality rates by S gene dropout status", 17, 18, bold=FALSE) %>%
        kable_styling(latex_options=c("scale_down", "hold_position"))
